---
title: "Presentation Slides"
author: "Yi Huang, YiyingWu"
date: "Junuary 13, 2024"
output:
  beamer_presentation:
    theme: "Madrid"
    colortheme: "default"
    fonttheme: "structurebold"
    slide_level: 2
    keep_tex: true
navigation: horizontal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Content

1.  Introduction

2.  Methodology

3.  Results

4.  Discussion

5.  References

## Introduction

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

##

`r kableExtra::text_spec("Methodology", color = "gray", bold = TRUE, font_size = 18)`

## Methodology

- Bullet 1
- Bullet 2
- Bullet 3

##

`r kableExtra::text_spec("Results", color = "gray", bold = TRUE, font_size = 18)`

## Results




## Discussion

```{r pressure}
plot(pressure)
```


## References
