---
title: "result"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 9, 
                      fig.height = 6,
                      out.width = "80%")
```

## This document shows the result of the code

## CardioStatsUSA
To install CardioStatsUSA, run this
```{r,eval=FALSE}
install.packages("CardioStatsUSA")
```
if not work, try this
```{r,eval=FALSE}
if (!requireNamespace("remotes", quietly = TRUE))
install.packages("remotes")
remotes::install_github("jhs-hwg/CardioStatsUSA")
```

## R packages
```{r,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# INSTALL PACKAGES
packages <- c("tidyverse", "dplyr", "knitr", "kableExtra", "cardioStatsUSA", 
              "survey", "gtsummary", "mice", "stargazer", "texreg", "jtools","haven")

# Install missing packages
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages], dependencies = TRUE)
}

# Load packages invisibly
invisible(lapply(packages, library, character.only = TRUE))

# # Remove variables associated with package installation
# rm(packages, installed_packages)
```


## data
```{r,warning=FALSE,message=FALSE}
# head(nhanes_data)
dat<-nhanes_data
```


## data cleaning

**combine categories**
```{r}
dat <- dat %>%
  mutate(
    # Demographics variables
    # demo_age_cat
    demo_age_cat = factor(case_when(
      demo_age_cat == "65 to 74" ~ "65+",  
      demo_age_cat == "75+" ~ "65+", 
      TRUE ~ demo_age_cat
    )),
    # demo_race
    demo_race=factor(case_when(
      demo_race == "Non-Hispanic Asian" ~ "Hispanic/Asian/Other",
      demo_race == "Hispanic" ~ "Hispanic/Asian/Other",
      demo_race == "Other" ~ "Hispanic/Asian/Other",
      TRUE ~ demo_race
    )),
    
    # Antihypertensive medication variables
    # bp_med_n_class
    bp_med_n_class=factor(case_when(
      bp_med_n_class == "Two" ~ "Two or more",
      bp_med_n_class == "Three" ~ "Two or more",
      bp_med_n_class == "Four or more" ~ "Two or more",
      TRUE ~ bp_med_n_class
    )),
    # bp_med_n_pills
    bp_med_n_pills=factor(case_when(
      bp_med_n_pills == "Two" ~ "Two or more",
      bp_med_n_pills == "Three" ~ "Two or more",
      bp_med_n_pills == "Four or more" ~ "Two or more",
      TRUE ~ bp_med_n_pills
    )),
    # cc_bmi
    cc_bmi=factor(case_when(
      cc_bmi == "30 to <35" ~ "30+",
      cc_bmi == "35+" ~ "30+",
      TRUE ~ cc_bmi
    )),
    # cc_smoke
    cc_smoke=factor(case_when(
      cc_smoke == "Former" ~ "Former",
      cc_smoke == "Current" ~ "Current",
      TRUE ~ cc_smoke
    ))
  )

```

### recode categorical data
```{r}
dat <- dat %>% mutate(
  # Demographics variables
  demo_age_cat=relevel(demo_age_cat, ref = "18 to 44"),
  demo_race=relevel(demo_race,ref="Non-Hispanic White"),
  pregnant=ifelse(demo_pregnant=="Yes",1,ifelse(demo_pregnant=="No",0,NA)),
  female=ifelse(demo_gender=="Women",1,ifelse(demo_gender=="Men",0,NA)),
  
  # Blood pressure variables
  bp_uncontrolled_140_90=ifelse(bp_uncontrolled_140_90=="Yes",1,ifelse(bp_uncontrolled_140_90=="No",0,NA)),
  bp_uncontrolled_130_80=ifelse(bp_uncontrolled_130_80=="Yes",1,ifelse(bp_uncontrolled_130_80=="No",0,NA)),
  
  # Hypertension variables
  htn_accaha=ifelse(htn_accaha=="Yes",1,ifelse(htn_accaha=="No",0,NA)),
  htn_aware=ifelse(htn_aware=="Yes",1,ifelse(htn_aware=="No",0,NA)),
  htn_resistant_jnc7=ifelse(htn_resistant_jnc7=="Yes",1,ifelse(htn_resistant_jnc7=="No",0,NA)),
  htn_resistant_accaha=ifelse(htn_resistant_accaha=="Yes",1,ifelse(htn_resistant_accaha=="No",0,NA)),
  htn_resistant_accaha_thz=ifelse(htn_resistant_accaha_thz=="Yes",1,ifelse(htn_resistant_accaha_thz=="No",0,NA)),
  htn_resistant_jnc7_thz=ifelse(htn_resistant_jnc7_thz=="Yes",1,ifelse(htn_resistant_jnc7_thz=="No",0,NA)),
  
  # Antihypertensive medication variables
  bp_med_use=ifelse(bp_med_use=="Yes",1,ifelse(bp_med_use=="No",0,NA)),
  bp_med_recommended_jnc7=ifelse(bp_med_recommended_jnc7=="Yes",1,ifelse(bp_med_recommended_jnc7=="No",0,NA)),
  bp_med_recommended_accaha=ifelse(bp_med_recommended_accaha=="Yes",1,ifelse(bp_med_recommended_accaha=="No",0,NA)),
  bp_med_recommended_escesh=ifelse(bp_med_recommended_escesh=="Yes",1,ifelse(bp_med_recommended_escesh=="No",0,NA)),
  bp_med_n_class=relevel(bp_med_n_class,ref="None"),
  bp_med_n_pills=relevel(bp_med_n_pills,ref="None"),
  bp_med_combination=ifelse(bp_med_combination=="Yes",1,ifelse(bp_med_combination=="No",0,NA)),
  bp_med_pills_gteq_2=ifelse(bp_med_pills_gteq_2=="Yes",1,ifelse(bp_med_pills_gteq_2=="No",0,NA)),
  bp_med_ace=ifelse(bp_med_ace=="Yes",1,ifelse(bp_med_ace=="No",0,NA)),
  bp_med_aldo=ifelse(bp_med_aldo=="Yes",1,ifelse(bp_med_aldo=="No",0,NA)),
  bp_med_alpha=ifelse(bp_med_alpha=="Yes",1,ifelse(bp_med_alpha=="No",0,NA)),
  bp_med_angioten=ifelse(bp_med_angioten=="Yes",1,ifelse(bp_med_angioten=="No",1,NA)),
  bp_med_beta=ifelse(bp_med_beta=="Yes",1,ifelse(bp_med_beta=="No",0,NA)),
  bp_med_ccb=ifelse(bp_med_ccb=="Yes",1,ifelse(bp_med_ccb=="No",0,NA)),
  bp_med_ccb_dh=ifelse(bp_med_ccb_dh=="Yes",1,ifelse(bp_med_ccb_dh=="No",0,NA)),
  bp_med_ccb_ndh=ifelse(bp_med_ccb_ndh=="Yes",1,ifelse(bp_med_ccb_ndh=="No",0,NA)),
  bp_med_central=ifelse(bp_med_central=="Yes",1,ifelse(bp_med_central=="No",0,NA)),
  bp_med_renin_inhibitors=ifelse(bp_med_renin_inhibitors=="Yes",1,ifelse(bp_med_renin_inhibitors=="No",0,NA)),
  bp_med_vasod=ifelse(bp_med_vasod=="Yes",1,ifelse(bp_med_vasod=="No",0,NA)),
  bp_med_diur_loop=ifelse(bp_med_diur_loop=="Yes",1,ifelse(bp_med_diur_loop=="No",0,NA)),
  bp_med_diur_Ksparing=ifelse(bp_med_diur_Ksparing=="Yes",1,ifelse(bp_med_diur_Ksparing=="No",0,NA)),
  bp_med_diur_thz=ifelse(bp_med_diur_thz=="Yes",1,ifelse(bp_med_diur_thz=="No",0,NA)),
  
  # Comorbidities variables
  cc_smoke=relevel(cc_smoke,ref="Current"),
  cc_bmi=relevel(cc_bmi,ref="<25"),
  cc_diabetes=ifelse(cc_diabetes=="Yes",1,ifelse(cc_diabetes=="No",0,NA)),
  cc_ckd=ifelse(cc_ckd=="Yes",1,ifelse(cc_ckd=="No",0,NA)),
  cc_cvd_mi=ifelse(cc_cvd_mi=="Yes",1,ifelse(cc_cvd_mi=="No",0,NA)),
  cc_cvd_chd=ifelse(cc_cvd_chd=="Yes",1,ifelse(cc_cvd_chd=="No",0,NA)),
  cc_cvd_stroke=ifelse(cc_cvd_stroke=="Yes",1,ifelse(cc_cvd_stroke=="No",0,NA)),
  cc_cvd_ascvd=ifelse(cc_cvd_ascvd=="Yes",1,ifelse(cc_cvd_ascvd=="No",0,NA)),
  cc_cvd_hf=ifelse(cc_cvd_hf=="Yes",1,ifelse(cc_cvd_hf=="No",0,NA)),
  cc_cvd_any=ifelse(cc_cvd_any=="Yes",1,ifelse(cc_cvd_any=="No",0,NA))
)
```

### select the relavent variables
```{r}
dat=dat%>%select(
  # Survey variables
  svy_id, svy_psu,svy_strata, svy_weight_mec, svy_subpop_htn,
  svy_year,
  # Demographics variables
  demo_age_cat, demo_age_years, demo_race, pregnant, female, 
  # Blood pressure variables
  bp_uncontrolled_140_90,bp_uncontrolled_130_80,
  # Hypertension variables
  htn_accaha, htn_aware, htn_resistant_accaha,
  htn_resistant_accaha_thz,
  # Antihypertensive medication variables
  bp_med_use, bp_med_recommended_accaha, bp_med_n_class,
  bp_med_n_pills, bp_med_combination, bp_med_pills_gteq_2,
  bp_med_ace, bp_med_aldo, bp_med_alpha, bp_med_angioten,
  bp_med_beta, bp_med_ccb, bp_med_ccb_dh, bp_med_ccb_ndh, 
  bp_med_central, bp_med_renin_inhibitors, bp_med_vasod,
  bp_med_diur_loop, bp_med_diur_Ksparing, bp_med_diur_thz, 
  # Comorbidities variables
  cc_smoke, cc_bmi, cc_diabetes, cc_ckd, cc_cvd_mi, cc_cvd_chd, 
  cc_cvd_stroke, cc_cvd_ascvd, cc_cvd_hf, cc_cvd_any
)
```

**check variables**
```{r}
## Summary Statistics
dat %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```

### Create a new data frame that contains 11 predictors
```{r}
my_dat <- dat %>% select(# Survey variables 
                         svy_id, svy_weight_mec, svy_psu, svy_strata, svy_year, svy_subpop_htn,
                         # outcome
                         bp_uncontrolled_140_90, bp_uncontrolled_130_80, 
                         # predictors
                         demo_age_years, demo_race, female, pregnant, cc_bmi, 
                         cc_diabetes, cc_ckd, cc_cvd_any, bp_med_use, htn_aware, cc_smoke
                         # bp_med_n_class, htn_resistant_jnc7
                        )

## Summary Statistics
my_dat %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```



### missing values

Participants with missing pregnancy status were assumed to be nonpregnant for these analyses.
reference: https://www.ahajournals.org/doi/10.1161/HYPERTENSIONAHA.123.20900


survey weights are calibrated within race, gender, and age groups to account for missing information on SBP, DBP or self-reported antihypertensive medication use: 
https://www.sciencedirect.com/science/article/pii/S027263860350004X?casa_token=U-KIitsxOGEAAAAA:jVZ1jyZmsVzR6BGEFVWUTjCh3wfKqvF1JXOLL55qFOu4Dk8giNQSfyU4pGS05Xl4DfM8uiwfPQ



```{r,eval=FALSE}
# Check the distribution of demo_age_years
hist(my_dat$demo_age_years, main="demo_age_years")

# adj for pregnant missing
my_dat <- my_dat %>% 
  mutate(pregnant = ifelse(is.na(pregnant), 0, pregnant))

# Initial imputation
ini = mice(my_dat, maxit = 0, print = FALSE)
pred0 = ini$pred
method0 = ini$method
method0
ini$nmis

# Study missing patterns in more details
md.pattern(my_dat,plot = FALSE)

# Modify the imputation predictor matrix
# and generate 5 imputations with 5 iterations 
# in each imputation using the modified predictor matrix
pred1 = pred0
pred1[, c("svy_id", "svy_weight_mec", "svy_psu", "svy_strata", "svy_year", "svy_subpop_htn")] = 0
pred1

# to Speed Up the Process, subset the data
# my_dat<-my_dat%>%filter(svy_subpop_chol == 1)
ini_1 = mice(my_dat, pred = pred1, m = 5, maxit = 5, print = FALSE, seed = 1)

# get the first imputed data set, use the complete( ) function
imp1 =  complete(ini_1, 1)

## Check the convergence of the model
plot(ini_1)

## Summary Statistics
imp1 %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```



# survey design
**Notes**: 

* combine weight in many years, refer to https://wwwn.cdc.gov/nchs/nhanes/tutorials/Weighting.aspx 
* The weight in the dataset is: **Full sample 2 year MEC exam weight** (2-year weight?)
* However, for all analyses that combine 1999-2000 with other survey cycles, you must start by using the 4-year weights provided by NCHS for 1999-2002, then include the 2-year weights for each additional 2-year cycle that is combined. (refer to larger nhance dataset to find 4-year weights???)

## weight adjustment for years
Since we must start by using the 4-year weights provided by NCHS for 1999-2002", and use 2-year weights for all observations from 1999-2016. Treat 2017-2020Mar as 3.2 years.

We refer to NHANES 1999-2000 and 2001-2002 and get the 4-year weights
```{r}
dat1<-read_xpt("./data/DEMO1999-2000.XPT")%>%
  janitor::clean_names()%>%
  select(seqn,wtmec4yr)%>%
  rename(svy_id=seqn)
dat2<-read_xpt("./data/DEMO2001-2002.XPT")%>%
  janitor::clean_names()%>%
  select(seqn,wtmec4yr)%>%
  rename(svy_id=seqn)
dat12<-rbind(dat1,dat2)

# dat12 %>% distinct(svy_id) %>% nrow()

# dat_new<-dat%>%filter(svy_year %in% c("1999-2000","2001-2002"))
my_dat <- my_dat %>% left_join(dat12, by = "svy_id")

#summary(dat$wtmec4yr)
#sum(is.na(dat$wtmec4yr))

my_dat<-my_dat%>%mutate(svy_weight_mec=ifelse(svy_year %in% c("1999-2000","2001-2002"),wtmec4yr,svy_weight_mec))

```


Combining nine survey cycles + one 3.2 year survey cycle (18+3.2 years: 1999-2016 2017-2020Mar)
```{r}
my_dat$svy_weight_mec<-ifelse(my_dat$svy_year %in% c("2017-2020"),my_dat$svy_weight_mec*3.2/21.2,ifelse(my_dat$svy_year %in% c("1999-2000","2001-2002"),my_dat$svy_weight_mec*4/21.2,my_dat$svy_weight_mec*2/21.2))
```

## define survey design
```{r}
nhanes_all<-svydesign(data=my_dat,id=~svy_id, strata=~svy_strata, weights=~svy_weight_mec, nest=TRUE)
```

## for blood pressure and hypertension sub-population
According to https://wwwn.cdc.gov/nchs/nhanes/tutorials/VarianceEstimation.aspx, As a general rule when working with complex survey data such as NHANES, you should never drop records from your analysis dataset before executing your analysis procedures. Instead, use the special statements provided in your software's analysis procedure to perform subgroup analyses.

We can use `subset` to produce correct variance estimates.

```{r}
nhanes<-subset(nhanes_all,svy_subpop_htn == 1)
```

# Plotting

All the variables used in plotting don't have any missing values.

## plot 1: Weighted Trend of Blood Pressure Control Over Time
show the trend of uncontrolled blood pressure over the years, accounting for survey design and weights.

```{r,fig.width = 10}
# calculating weighted proportions for each year
bp_trends1 <- svyby(~bp_uncontrolled_140_90, ~svy_year, nhanes, svymean, na.rm = TRUE)
bp_trends2 <- svyby(~bp_uncontrolled_130_80, ~svy_year, nhanes, svymean, na.rm = TRUE)

# Melting the data for plotting
bp_trends_df1 <- reshape2::melt(bp_trends1)
bp_trends_df2 <- reshape2::melt(bp_trends2)
bp_trends_df1<-bp_trends_df1[1:10,]
bp_trends_df2<-bp_trends_df2[1:10,]
bp_trends_df <- rbind(bp_trends_df1,bp_trends_df2)

# Changing the levels of the 'variable' column
bp_trends_df$variable <- ifelse(bp_trends_df$variable=="bp_uncontrolled_140_90", "SBP>=140mmHg or DBP>=90mmHg", "SBP>=130mmHg or DBP>=80mmHg")

# Plotting with a bar plot
ggplot(bp_trends_df, aes(x = svy_year, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = position_stack(), width = 0.7) +
  theme_minimal() +
  labs(title = "Trend of Uncontrolled Blood Pressure Over Years (Weighted)",
       x = "NHANES cycle",
       y = "Proportion Uncontrolled (Weighted)",
       fill = "Blood Pressure Uncontrol")

```

## plot 2: Weighted Distribution of Blood Pressure Control by race
```{r}
# Calculating weighted counts for each race and blood pressure uncontrol status
bp_race_dist1 <- svyby(~bp_uncontrolled_140_90, ~demo_race, nhanes, svymean, na.rm = TRUE)
bp_race_dist2 <- svyby(~bp_uncontrolled_130_80, ~demo_race, nhanes, svymean, na.rm = TRUE)

# Melting the data for plotting
bp_race_dist_melted1 <- reshape2::melt(bp_race_dist1, id.vars = "demo_race")
bp_race_dist_melted2 <- reshape2::melt(bp_race_dist2, id.vars = "demo_race")
bp_race_dist_melted1<-bp_race_dist_melted1[1:3,]
bp_race_dist_melted2<-bp_race_dist_melted2[1:3,]
bp_race_dist_melted<-rbind(bp_race_dist_melted1,bp_race_dist_melted2)

# Changing the levels of the 'variable' column
bp_race_dist_melted$variable <- ifelse(bp_race_dist_melted$variable=="bp_uncontrolled_140_90", "SBP>=140mmHg or DBP>=90mmHg", "SBP>=130mmHg or DBP>=80mmHg")

# Plotting
ggplot(bp_race_dist_melted, aes(x = demo_race, y = value, fill = variable)) +
  geom_bar(stat = "identity", position = position_stack()) +
  theme_minimal()+
  labs(title = "Distribution of Blood Pressure Uncontrol by Race (Weighted)",
       x = "Race",
       y = "Proportion (Weighted)",
       fill = "Blood Pressure Uncontrol")

```


# Doing Imputation and logistic regression at the Same Time
```{r}
# adj for pregnant missing
my_dat <- my_dat %>% 
  mutate(pregnant = ifelse(is.na(pregnant), 0, pregnant))

#create five imputations. The imputations object contains all five
#complete datasets.
imputations <- mice(my_dat, 5, printFlag=FALSE)

lm_svy_mi <- function(formula, imputations) {
  
  #setting up null objects allows us to easily add results
  #later
  b <- se <- R2MF <- R2CU <-NULL
  aic <- NULL
  mean.aic <- NULL
  # AUC <- mean.AUC <-NULL
  
  #now loop through our imputations and run the model
  for(i in 1:imputations$m) {
    #grab the complete dataset
    imputation <- complete(imputations, i)
    #create the design effect object
    svy <- svydesign(data=my_dat,id=~svy_id, strata=~svy_strata, weights=~svy_weight_mec, nest=TRUE)
    imputation.svy<-subset(svy,svy_subpop_htn == 1)
    #run the model
    model <- svyglm(formula, design=imputation.svy,family=quasibinomial)
    #collect the results
    b <- cbind(b, coef(model))
    se <- cbind(se, summary(model)$coef[,2])
    
    summ_model <- summ(model)
      
    # # McFadden's R-squared
    R2MF <- attr(summ_model, which = "rsqmc")
    
    # # CRagg-Uhler R-squared
    R2CU <- attr(summ_model, which = "rsq")
    
    # AIC
    aic <- c(aic,(-2) * logLik(model) + 2 * length(coef(model)))
    
    # # Logistic Regression AUC calculation
    #predictions <- predict(model, type = "response")
    #ROC_res <- roc(imputation.svy$variables$bp_uncontrolled_140_90, predictions)  # Replace with dependent variable
    #AUC <- c(AUC, auc(ROC_res))
    
  }
  
  #now pool the results
  b.pool <- apply(b, 1, mean)
  between.var <- apply(b, 1, var)
  within.var <- apply(se^2, 1, mean)
  se.pool <- sqrt(within.var+between.var+between.var/imputations$m) 
  lower.ci <- b.pool - 1.96 * se.pool  # Lower bound of 95% CI
  upper.ci <- b.pool + 1.96 * se.pool  # Upper bound of 95% CI
  t.pool <- b.pool/se.pool 
  pvalue.pool <- (1-pnorm(abs(t.pool)))*2 
  coefficients <- data.frame(b.pool, se.pool, lower.ci, upper.ci, t.pool, pvalue.pool)
  
  #we can also grap n and p from the last model since 
  #they should be the same across all iterations
  n <- nobs(model)
  p <- length(model$coefficients)-1
  mean.R2MF <- mean(R2MF)
  mean.R2CU <- mean(R2CU)
  mean.aic <- mean(aic)
  #mean.AUC <- mean(AUC)
  
  #return everything in a list
  return(list(coef=coefficients,
              n=n,
              R2MF = mean.R2MF,
              R2CU = mean.R2CU,
              aic = mean.aic
              )
         )
}
```

```{r}
# check model fit based on SL
convertModel <- function(model) {
  tr <- createTexreg(
    coef.names = rownames(model$coef),
    coef = model$coef$b.pool,
    se = model$coef$se.pool,
    ci.low = model$coef$lower.ci,
    ci.up = model$coef$upper.ci,
    pvalues = model$coef$pvalue.pool,
    gof.names=c("McFadden's R-squared", "Ragg-Uhler's R-squared","Mean AIC"),
    gof = c(model$R2MF, model$R2CU,model$aic),
    gof.decimal = c(TRUE,TRUE,TRUE)
  )
}

# Stage 2 Hypertension
#now lets try the model out
model1 <- lm_svy_mi(bp_uncontrolled_140_90~svy_year+demo_age_years+demo_race+female+cc_bmi+cc_diabetes+cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke, imputations)

# create a few models to compare model fit
# 11 predictors
model2 <- lm_svy_mi(bp_uncontrolled_140_90 ~ demo_age_years + demo_race + female + pregnant + cc_bmi +
                      cc_diabetes + cc_ckd + cc_cvd_any + bp_med_use + htn_aware + 
                      cc_smoke, imputations)
# final 10 predictors
model3 <- lm_svy_mi(bp_uncontrolled_140_90 ~ svy_year + demo_age_years + demo_race + female + cc_bmi + 
                      cc_diabetes + cc_ckd + cc_cvd_any + bp_med_use + htn_aware, imputations)

# Stage 1 Hypertension
#now lets try the model out
model_s1 <- lm_svy_mi(bp_uncontrolled_130_80 ~ svy_year + demo_age_years + demo_race + female + cc_bmi + 
                        cc_diabetes + cc_ckd + cc_cvd_any + bp_med_use + htn_aware, imputations)
model_s1
```

```{r model 1}
# stage 2 hypertension
screenreg(convertModel(model3))

# stage 1 hypertension
screenreg(convertModel(model_s1))
```

```{r model 3}
screenreg(convertModel(model3))
```

# plot OR and 95% CI
```{r}
# first create res dataframe
res_df<-function(model){
    coef.names = rownames(model$coef)
    OR = exp(model$coef$b.pool)
    ci.low = exp(model$coef$lower.ci)
    ci.up = exp(model$coef$upper.ci)
    res<-data_frame(coef.names,OR,ci.low,ci.up)
    return(res)
}
res_m1<-res_df(model_s1)
res_m2<-res_df(model3)

# plot
plot_or<-function(df,title){
  res<-ggplot(df, aes(x = coef.names, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = ci.low, ymax = ci.up), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dotted", color = "red") +  # Add vertical line
  coord_flip() +  # Flip the axes for a horizontal plot
  theme_minimal() +
  labs(title = title,
       x = "Variables",
       y = "Odds Ratio")
  return(res)
}
  
plot_or(res_m1,"Odds Ratios and 95% Confidence Intervals for Model1")
plot_or(res_m2,"Odds Ratios and 95% Confidence Intervals for Model2")
```


if not doing imputation
```{r}
fit1<-svyglm(bp_uncontrolled_140_90~svy_year+demo_age_years+demo_race+female+pregnant+cc_bmi+
              cc_diabetes+cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke,
            design=nhanes,family=quasibinomial)

summary(fit1)

fit2<-svyglm(bp_uncontrolled_130_80~svy_year+demo_age_years+demo_race+female+pregnant+cc_bmi+
              cc_diabetes+cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke,
            design=nhanes,family=quasibinomial)

summary(fit2)
```



# Lasso logistic

