---
title: "result"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## This document shows the result of the code

## CardioStatsUSA
To install CardioStatsUSA, run this
```{r,eval=FALSE}
install.packages("CardioStatsUSA")
```
if not work, try this
```{r,eval=FALSE}
if (!requireNamespace("remotes", quietly = TRUE))
install.packages("remotes")
remotes::install_github("jhs-hwg/CardioStatsUSA")
```

## R packages
```{r,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# INSTALL PACKAGES
packages <- c("tidyverse", "dplyr", "knitr", "kableExtra", "cardioStatsUSA", 
              "survey", "gtsummary", "mice", "stargazer", "texreg", "pROC")

# Install missing packages
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages], dependencies = TRUE)
}

# Load packages invisibly
invisible(lapply(packages, library, character.only = TRUE))

# Remove variables associated with package installation
rm(packages, installed_packages)
```


## data
```{r,warning=FALSE,message=FALSE}
# head(nhanes_data)
dat<-nhanes_data
```


## data cleaning

**combine categories**
```{r}
dat <- dat %>%
  mutate(
    # Demographics variables
    # demo_age_cat
    demo_age_cat = factor(case_when(
      demo_age_cat == "65 to 74" ~ "65+",  
      demo_age_cat == "75+" ~ "65+", 
      TRUE ~ demo_age_cat
    )),
    # demo_race
    demo_race=factor(case_when(
      demo_race == "Non-Hispanic Asian" ~ "Hispanic/Asian/Other",
      demo_race == "Hispanic" ~ "Hispanic/Asian/Other",
      demo_race == "Other" ~ "Hispanic/Asian/Other",
      TRUE ~ demo_race
    )),
    
    # Antihypertensive medication variables
    # bp_med_n_class
    bp_med_n_class=factor(case_when(
      bp_med_n_class == "Two" ~ "Two or more",
      bp_med_n_class == "Three" ~ "Two or more",
      bp_med_n_class == "Four or more" ~ "Two or more",
      TRUE ~ bp_med_n_class
    )),
    # bp_med_n_pills
    bp_med_n_pills=factor(case_when(
      bp_med_n_pills == "Two" ~ "Two or more",
      bp_med_n_pills == "Three" ~ "Two or more",
      bp_med_n_pills == "Four or more" ~ "Two or more",
      TRUE ~ bp_med_n_pills
    )),
    # cc_bmi
    cc_bmi=factor(case_when(
      cc_bmi == "30 to <35" ~ "30+",
      cc_bmi == "35+" ~ "30+",
      TRUE ~ cc_bmi
    )),
    # cc_smoke
    cc_smoke=factor(case_when(
      cc_smoke == "Former" ~ "Former/Current",
      cc_smoke == "Current" ~ "Former/Current",
      TRUE ~ cc_smoke
    ))
  )

```

### recode categorical data
```{r}
dat <- dat %>% mutate(
  # Demographics variables
  demo_age_cat=relevel(demo_age_cat, ref = "18 to 44"),
  demo_race=relevel(demo_race,ref="Non-Hispanic White"),
  pregnant=ifelse(demo_pregnant=="Yes",1,ifelse(demo_pregnant=="No",0,NA)),
  female=ifelse(demo_gender=="Women",1,ifelse(demo_gender=="Men",0,NA)),
  
  # Blood pressure variables
  bp_uncontrolled_140_90=ifelse(bp_uncontrolled_140_90=="Yes",1,ifelse(bp_uncontrolled_140_90=="No",0,NA)),
  bp_uncontrolled_130_80=ifelse(bp_uncontrolled_130_80=="Yes",1,ifelse(bp_uncontrolled_130_80=="No",0,NA)),
  
  # Hypertension variables
  htn_accaha=ifelse(htn_accaha=="Yes",1,ifelse(htn_accaha=="No",0,NA)),
  htn_aware=ifelse(htn_aware=="Yes",1,ifelse(htn_aware=="No",0,NA)),
  htn_resistant_jnc7=ifelse(htn_resistant_jnc7=="Yes",1,ifelse(htn_resistant_jnc7=="No",0,NA)),
  htn_resistant_accaha=ifelse(htn_resistant_accaha=="Yes",1,ifelse(htn_resistant_accaha=="No",0,NA)),
  htn_resistant_accaha_thz=ifelse(htn_resistant_accaha_thz=="Yes",1,ifelse(htn_resistant_accaha_thz=="No",0,NA)),
  htn_resistant_jnc7_thz=ifelse(htn_resistant_jnc7_thz=="Yes",1,ifelse(htn_resistant_jnc7_thz=="No",0,NA)),
  
  # Antihypertensive medication variables
  bp_med_use=ifelse(bp_med_use=="Yes",1,ifelse(bp_med_use=="No",0,NA)),
  bp_med_recommended_jnc7=ifelse(bp_med_recommended_jnc7=="Yes",1,ifelse(bp_med_recommended_jnc7=="No",0,NA)),
  bp_med_recommended_accaha=ifelse(bp_med_recommended_accaha=="Yes",1,ifelse(bp_med_recommended_accaha=="No",0,NA)),
  bp_med_recommended_escesh=ifelse(bp_med_recommended_escesh=="Yes",1,ifelse(bp_med_recommended_escesh=="No",0,NA)),
  bp_med_n_class=relevel(bp_med_n_class,ref="None"),
  bp_med_n_pills=relevel(bp_med_n_pills,ref="None"),
  bp_med_combination=ifelse(bp_med_combination=="Yes",1,ifelse(bp_med_combination=="No",0,NA)),
  bp_med_pills_gteq_2=ifelse(bp_med_pills_gteq_2=="Yes",1,ifelse(bp_med_pills_gteq_2=="No",0,NA)),
  bp_med_ace=ifelse(bp_med_ace=="Yes",1,ifelse(bp_med_ace=="No",0,NA)),
  bp_med_aldo=ifelse(bp_med_aldo=="Yes",1,ifelse(bp_med_aldo=="No",0,NA)),
  bp_med_alpha=ifelse(bp_med_alpha=="Yes",1,ifelse(bp_med_alpha=="No",0,NA)),
  bp_med_angioten=ifelse(bp_med_angioten=="Yes",1,ifelse(bp_med_angioten=="No",1,NA)),
  bp_med_beta=ifelse(bp_med_beta=="Yes",1,ifelse(bp_med_beta=="No",0,NA)),
  bp_med_ccb=ifelse(bp_med_ccb=="Yes",1,ifelse(bp_med_ccb=="No",0,NA)),
  bp_med_ccb_dh=ifelse(bp_med_ccb_dh=="Yes",1,ifelse(bp_med_ccb_dh=="No",0,NA)),
  bp_med_ccb_ndh=ifelse(bp_med_ccb_ndh=="Yes",1,ifelse(bp_med_ccb_ndh=="No",0,NA)),
  bp_med_central=ifelse(bp_med_central=="Yes",1,ifelse(bp_med_central=="No",0,NA)),
  bp_med_renin_inhibitors=ifelse(bp_med_renin_inhibitors=="Yes",1,ifelse(bp_med_renin_inhibitors=="No",0,NA)),
  bp_med_vasod=ifelse(bp_med_vasod=="Yes",1,ifelse(bp_med_vasod=="No",0,NA)),
  bp_med_diur_loop=ifelse(bp_med_diur_loop=="Yes",1,ifelse(bp_med_diur_loop=="No",0,NA)),
  bp_med_diur_Ksparing=ifelse(bp_med_diur_Ksparing=="Yes",1,ifelse(bp_med_diur_Ksparing=="No",0,NA)),
  bp_med_diur_thz=ifelse(bp_med_diur_thz=="Yes",1,ifelse(bp_med_diur_thz=="No",0,NA)),
  
  # Comorbidities variables
  cc_smoke=relevel(cc_smoke,ref="Never"),
  cc_bmi=relevel(cc_bmi,ref="<25"),
  cc_diabetes=ifelse(cc_diabetes=="Yes",1,ifelse(cc_diabetes=="No",0,NA)),
  cc_ckd=ifelse(cc_ckd=="Yes",1,ifelse(cc_ckd=="No",0,NA)),
  cc_cvd_mi=ifelse(cc_cvd_mi=="Yes",1,ifelse(cc_cvd_mi=="No",0,NA)),
  cc_cvd_chd=ifelse(cc_cvd_chd=="Yes",1,ifelse(cc_cvd_chd=="No",0,NA)),
  cc_cvd_stroke=ifelse(cc_cvd_stroke=="Yes",1,ifelse(cc_cvd_stroke=="No",0,NA)),
  cc_cvd_ascvd=ifelse(cc_cvd_ascvd=="Yes",1,ifelse(cc_cvd_ascvd=="No",0,NA)),
  cc_cvd_hf=ifelse(cc_cvd_hf=="Yes",1,ifelse(cc_cvd_hf=="No",0,NA)),
  cc_cvd_any=ifelse(cc_cvd_any=="Yes",1,ifelse(cc_cvd_any=="No",0,NA))
)
```

### select the relavent variables
```{r}
dat=dat%>%select(
  # Survey variables
  svy_id, svy_psu,svy_strata, svy_weight_mec, svy_subpop_htn,
  svy_year,
  # Demographics variables
  demo_age_cat, demo_age_years, demo_race, pregnant, female, 
  # Blood pressure variables
  bp_uncontrolled_140_90,bp_uncontrolled_130_80,
  # Hypertension variables
  htn_accaha, htn_aware, htn_resistant_accaha,
  htn_resistant_accaha_thz,
  # Antihypertensive medication variables
  bp_med_use, bp_med_recommended_accaha, bp_med_n_class,
  bp_med_n_pills, bp_med_combination, bp_med_pills_gteq_2,
  bp_med_ace, bp_med_aldo, bp_med_alpha, bp_med_angioten,
  bp_med_beta, bp_med_ccb, bp_med_ccb_dh, bp_med_ccb_ndh, 
  bp_med_central, bp_med_renin_inhibitors, bp_med_vasod,
  bp_med_diur_loop, bp_med_diur_Ksparing, bp_med_diur_thz, 
  # Comorbidities variables
  cc_smoke, cc_bmi, cc_diabetes, cc_ckd, cc_cvd_mi, cc_cvd_chd, 
  cc_cvd_stroke, cc_cvd_ascvd, cc_cvd_hf, cc_cvd_any
)
```

**check variables**
```{r}
## Summary Statistics
dat %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```

### Create a new data frame that contains 11 predictors
```{r}
my_dat <- dat %>% select(# Survey variables 
                         svy_id, svy_weight_mec, svy_psu, svy_strata, svy_year, svy_subpop_htn,
                         # outcome
                         bp_uncontrolled_140_90, bp_uncontrolled_130_80, 
                         # predictors
                         demo_age_years, demo_race, female, pregnant, cc_bmi, 
                         cc_diabetes, cc_ckd, cc_cvd_any, bp_med_use, htn_aware, cc_smoke
                         # bp_med_n_class, htn_resistant_jnc7
                        )

## Summary Statistics
my_dat %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```



### missing values

Participants with missing pregnancy status were assumed to be nonpregnant for these analyses.
reference: https://www.ahajournals.org/doi/10.1161/HYPERTENSIONAHA.123.20900


survey weights are calibrated within race, gender, and age groups to account for missing information on SBP, DBP or self-reported antihypertensive medication use: 
https://www.sciencedirect.com/science/article/pii/S027263860350004X?casa_token=U-KIitsxOGEAAAAA:jVZ1jyZmsVzR6BGEFVWUTjCh3wfKqvF1JXOLL55qFOu4Dk8giNQSfyU4pGS05Xl4DfM8uiwfPQ



```{r,eval=FALSE}
# Check the distribution of demo_age_years
hist(my_dat$demo_age_years, main="demo_age_years")

# adj for pregnant missing
my_dat <- my_dat %>% 
  mutate(pregnant = ifelse(is.na(pregnant), 0, pregnant))

# Initial imputation
ini = mice(my_dat, maxit = 0, print = FALSE)
pred0 = ini$pred
method0 = ini$method
method0
ini$nmis

# Study missing patterns in more details
md.pattern(my_dat,plot = FALSE)

# Modify the imputation predictor matrix
# and generate 5 imputations with 5 iterations 
# in each imputation using the modified predictor matrix
pred1 = pred0
pred1[, c("svy_id", "svy_weight_mec", "svy_psu", "svy_strata", "svy_year", "svy_subpop_htn")] = 0
pred1

# to Speed Up the Process, subset the data
# my_dat<-my_dat%>%filter(svy_subpop_chol == 1)
ini_1 = mice(my_dat, pred = pred1, m = 5, maxit = 5, print = FALSE, seed = 1)

# get the first imputed data set, use the complete( ) function
imp1 =  complete(ini_1, 1)

## Check the convergence of the model
plot(ini_1)

## Summary Statistics
imp1 %>% 
  select(everything()) %>% 
  tbl_summary() %>% 
  bold_labels()
```



# survey design
**Notes**: 

* combine weight in many years, refer to https://wwwn.cdc.gov/nchs/nhanes/tutorials/Weighting.aspx 
* The weight in the dataset is: **Full sample 2 year MEC exam weight** (2-year weight?)
* However, for all analyses that combine 1999-2000 with other survey cycles, you must start by using the 4-year weights provided by NCHS for 1999-2002, then include the 2-year weights for each additional 2-year cycle that is combined. (refer to larger nhance dataset to find 4-year weights???)

## weight adjustment for years
To simplify this, we first ignore the "must start by using the 4-year weights provided by NCHS for 1999-2002", and use 2-year weights for all observations from 1999-2016. Treat 2017-2020Mar as 3.2 years.

Combining nine survey cycles + one 3.2 year survey cycle (18+3.2 years: 1999-2016 2017-2020Mar)
```{r}
my_dat$svy_weight_mec<-ifelse(my_dat$svy_year %in% c("2017-2020"),my_dat$svy_weight_mec*3.2/21.2,my_dat$svy_weight_mec*2/21.2)
```

## define survey design
```{r}
nhanes_all<-svydesign(data=my_dat,id=~svy_id, strata=~svy_strata, weights=~svy_weight_mec, nest=TRUE)
```

## for blood pressure and hypertension sub-population
According to https://wwwn.cdc.gov/nchs/nhanes/tutorials/VarianceEstimation.aspx, As a general rule when working with complex survey data such as NHANES, you should never drop records from your analysis dataset before executing your analysis procedures. Instead, use the special statements provided in your software's analysis procedure to perform subgroup analyses.

We can use `subset` to produce correct variance estimates.

```{r}
nhanes<-subset(nhanes_all,svy_subpop_htn == 1)
```



# Doing Imputation and logistic regression at the Same Time
```{r}
# adj for pregnant missing
my_dat <- my_dat %>% 
  mutate(pregnant = ifelse(is.na(pregnant), 0, pregnant))

#create five imputations. The imputations object contains all five
#complete datasets.
imputations <- mice(my_dat, 5, printFlag=FALSE)

lm_svy_mi <- function(formula, imputations) {
  
  #setting up null objects allows us to easily add results
  #later
  b <- se <- NULL
  
  #now loop through our imputations and run the model
  for(i in 1:imputations$m) {
    #grab the complete dataset
    imputation <- complete(imputations, i)
    #create the design effect object
    svy <- svydesign(data=my_dat,id=~svy_id, strata=~svy_strata, weights=~svy_weight_mec, nest=TRUE)
    imputation.svy<-subset(svy,svy_subpop_htn == 1)
    #run the model
    model <- svyglm(formula, design=imputation.svy,family=quasibinomial)
    #collect the results
    b <- cbind(b, coef(model))
    se <- cbind(se, summary(model)$coef[,2])
    
    # # McFadden's R-squared
    # null_model <- svyglm(response~1, design = imputation.svy, family = quasibinomial)
    # ll_full <- logLik(model)
    # ll_null <- logLik(null_model)
    # R2 <- c(R2, 1 - (ll_full/ll_null))
    
    # # Logistic Regression AUC calculation
    # predictions <- predict(model, type = "response")
    # ROC_res <- roc(imputation$dependent_variable, predictions)  # Replace with dependent variable
    # AUC <- c(AUC, auc(ROC_res))
  }
  
  #now pool the results
  b.pool <- apply(b, 1, mean)
  between.var <- apply(b, 1, var)
  within.var <- apply(se^2, 1, mean)
  se.pool <- sqrt(within.var+between.var+between.var/imputations$m) 
  t.pool <- b.pool/se.pool 
  pvalue.pool <- (1-pnorm(abs(t.pool)))*2 
  coefficients <- data.frame(b.pool, se.pool, t.pool, pvalue.pool)
  
  #we can also grap n and p from the last model since 
  #they should be the same across all iterations
  n <- nobs(model)
  p <- length(model$coefficients)-1
  # mean.R2 <- mean(R2)
  # mean.AUC <- mean(AUC)
  
  #return everything in a list
  return(list(coef=coefficients,
              n=n
              # , 
              # R2 = mean.R2, 
              # AUC = mean.AUC
              )
         )
}
```

```{r}
#now lets try the model out
model1 <- lm_svy_mi(bp_uncontrolled_140_90~svy_year+demo_age_years+demo_race+female+pregnant+cc_bmi+cc_diabetes+cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke, imputations)

# check model fit based on SL
convertModel <- function(model) {
  tr <- createTexreg(
    coef.names = rownames(model$coef), 
    coef = model$coef$b.pool, 
    se = model$coef$se.pool, 
    pvalues = model$coef$pvalue.pool,
    # gof.names = c("Mean AUC"),
    # gof = c( model$AUC),
    # gof.decimal = c(TRUE)
  )
}

#To show how this looks lets create a few models
model2 <- lm_svy_mi(bp_uncontrolled_140_90~demo_age_years+demo_race+female+cc_bmi+cc_diabetes
                    +cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke, imputations)

screenreg(convertModel(model1))
screenreg(convertModel(model2))
```

if not doing imputation
```{r}
fit<-svyglm(bp_uncontrolled_140_90~svy_year+demo_age_years+demo_race+female+pregnant+cc_bmi+
              cc_diabetes+cc_ckd+cc_cvd_any+bp_med_use+htn_aware+cc_smoke,
            design=nhanes,family=quasibinomial)

summary(fit)
```


# Lasso logistic

