---
title: "result"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This document shows the result of the code

## CardioStatsUSA
To install CardioStatsUSA, run this
```{r,eval=FALSE}
install.packages("CardioStatsUSA")
```
if not work, try this
```{r,eval=FALSE}
if (!requireNamespace("remotes", quietly = TRUE))
install.packages("remotes")
remotes::install_github("jhs-hwg/CardioStatsUSA")
```

## data
```{r,warning=FALSE,message=FALSE}
library(cardioStatsUSA)
library(tidyverse)
library(survey)
library(gtsummary)
# head(nhanes_data)
dat<-nhanes_data
```


## data cleaning

### missing values

### recode categorical data
```{r}
dat <- dat %>% mutate(
  # Demographics variables
  demo_age_cat=relevel(demo_age_cat, ref = "18 to 44"),
  demo_race=relevel(demo_race,ref="Non-Hispanic White"),
  pregnant=ifelse(demo_pregnant=="Yes",1,ifelse(demo_pregnant=="No",0,NA)),
  female=ifelse(demo_gender=="Women",1,ifelse(demo_gender=="Men",0,NA)),
  
  # Blood pressure variables
  bp_uncontrolled_140_90=ifelse(bp_uncontrolled_140_90=="Yes",1,ifelse(bp_uncontrolled_140_90=="No",0,NA)),
  bp_uncontrolled_130_80=ifelse(bp_uncontrolled_130_80=="Yes",1,ifelse(bp_uncontrolled_130_80=="No",0,NA)),
  
  # Hypertension variables
  htn_accaha=ifelse(htn_accaha=="Yes",1,ifelse(htn_accaha=="No",0,NA)),
  htn_aware=ifelse(htn_aware=="Yes",1,ifelse(htn_aware=="No",0,NA)),
  htn_resistant_jnc7=ifelse(htn_resistant_jnc7=="Yes",1,ifelse(htn_resistant_jnc7=="No",0,NA)),
  htn_resistant_accaha=ifelse(htn_resistant_accaha=="Yes",1,ifelse(htn_resistant_accaha=="No",0,NA)),
  htn_resistant_accaha_thz=ifelse(htn_resistant_accaha_thz=="Yes",1,ifelse(htn_resistant_accaha_thz=="No",0,NA)),
  htn_resistant_jnc7_thz=ifelse(htn_resistant_jnc7_thz=="Yes",1,ifelse(htn_resistant_jnc7_thz=="No",0,NA)),
  
  # Antihypertensive medication variables
  bp_med_use=ifelse(bp_med_use=="Yes",1,ifelse(bp_med_use=="No",0,NA)),
  bp_med_recommended_jnc7=ifelse(bp_med_recommended_jnc7=="Yes",1,ifelse(bp_med_recommended_jnc7=="No",0,NA)),
  bp_med_recommended_accaha=ifelse(bp_med_recommended_accaha=="Yes",1,ifelse(bp_med_recommended_accaha=="No",0,NA)),
  bp_med_recommended_escesh=ifelse(bp_med_recommended_escesh=="Yes",1,ifelse(bp_med_recommended_escesh=="No",0,NA)),
  bp_med_n_class=relevel(bp_med_n_class,ref="None"),
  bp_med_n_pills=relevel(bp_med_n_pills,ref="None"),
  bp_med_combination=ifelse(bp_med_combination=="Yes",1,ifelse(bp_med_combination=="No",0,NA)),
  bp_med_pills_gteq_2=ifelse(bp_med_pills_gteq_2=="Yes",1,ifelse(bp_med_pills_gteq_2=="No",0,NA)),
  bp_med_ace=ifelse(bp_med_ace=="Yes",1,ifelse(bp_med_ace=="No",0,NA)),
  bp_med_aldo=ifelse(bp_med_aldo=="Yes",1,ifelse(bp_med_aldo=="No",0,NA)),
  bp_med_alpha=ifelse(bp_med_alpha=="Yes",1,ifelse(bp_med_alpha=="No",0,NA)),
  bp_med_angioten=ifelse(bp_med_angioten=="Yes",1,ifelse(bp_med_angioten=="No",1,NA)),
  bp_med_beta=ifelse(bp_med_beta=="Yes",1,ifelse(bp_med_beta=="No",0,NA)),
  bp_med_ccb=ifelse(bp_med_ccb=="Yes",1,ifelse(bp_med_ccb=="No",0,NA)),
  bp_med_ccb_dh=ifelse(bp_med_ccb_dh=="Yes",1,ifelse(bp_med_ccb_dh=="No",0,NA)),
  bp_med_ccb_ndh=ifelse(bp_med_ccb_ndh=="Yes",1,ifelse(bp_med_ccb_ndh=="No",0,NA)),
  bp_med_central=ifelse(bp_med_central=="Yes",1,ifelse(bp_med_central=="No",0,NA)),
  bp_med_renin_inhibitors=ifelse(bp_med_renin_inhibitors=="Yes",1,ifelse(bp_med_renin_inhibitors=="No",0,NA)),
  bp_med_vasod=ifelse(bp_med_vasod=="Yes",1,ifelse(bp_med_vasod=="No",0,NA)),
  bp_med_diur_loop=ifelse(bp_med_diur_loop=="Yes",1,ifelse(bp_med_diur_loop=="No",0,NA)),
  bp_med_diur_Ksparing=ifelse(bp_med_diur_Ksparing=="Yes",1,ifelse(bp_med_diur_Ksparing=="No",0,NA)),
  bp_med_diur_thz=ifelse(bp_med_diur_thz=="Yes",1,ifelse(bp_med_diur_thz=="No",0,NA)),
  
  # Comorbidities variables
  cc_smoke=relevel(cc_smoke,ref="Never"),
  cc_bmi=relevel(cc_bmi,ref="<25"),
  cc_diabetes=ifelse(cc_diabetes=="Yes",1,ifelse(cc_diabetes=="No",0,NA)),
  cc_ckd=ifelse(cc_ckd=="Yes",1,ifelse(cc_ckd=="No",0,NA)),
  cc_cvd_mi=ifelse(cc_cvd_mi=="Yes",1,ifelse(cc_cvd_mi=="No",0,NA)),
  cc_cvd_chd=ifelse(cc_cvd_chd=="Yes",1,ifelse(cc_cvd_chd=="No",0,NA)),
  cc_cvd_stroke=ifelse(cc_cvd_stroke=="Yes",1,ifelse(cc_cvd_stroke=="No",0,NA)),
  cc_cvd_ascvd=ifelse(cc_cvd_ascvd=="Yes",1,ifelse(cc_cvd_ascvd=="No",0,NA)),
  cc_cvd_hf=ifelse(cc_cvd_hf=="Yes",1,ifelse(cc_cvd_hf=="No",0,NA)),
  cc_cvd_any=ifelse(cc_cvd_any=="Yes",1,ifelse(cc_cvd_any=="No",0,NA))
)
```

**check variables**
```{r}
# summary(dat$demo_age_cat)
# dat$pregnant=as.factor(dat$pregnant)
# summary(dat$pregnant)
# dat$female=as.factor(dat$female)
# summary(dat$female)
# summary(dat$bp_med_n_class)
# dat$htn_accaha=as.factor(dat$htn_accaha)
# summary(dat$htn_accaha)
# summary(dat$bp_med_n_pills)

## Summary Statistics
dat %>% 
  select(demo_age_cat, pregnant, female, bp_med_n_class, htn_accaha, htn_accaha, bp_med_n_pills) %>% 
  tbl_summary() %>% 
  bold_labels()
```


# survey design
**Notes**: 

* combine weight in many years, refer to https://wwwn.cdc.gov/nchs/nhanes/tutorials/Weighting.aspx 
* The weight in the dataset is: **Full sample 2 year MEC exam weight** (2-year weight?)
* However, for all analyses that combine 1999-2000 with other survey cycles, you must start by using the 4-year weights provided by NCHS for 1999-2002, then include the 2-year weights for each additional 2-year cycle that is combined. (refer to larger nhance dataset to find 4-year weights???)
```{r}
nhanes_all<-svydesign(data=dat,id=~svy_id, strata=~svy_strata, weights=~svy_weight_mec, nest=TRUE)
```

## for blood pressure and hypertension sub-population
According to https://wwwn.cdc.gov/nchs/nhanes/tutorials/VarianceEstimation.aspx, As a general rule when working with complex survey data such as NHANES, you should never drop records from your analysis dataset before executing your analysis procedures. Instead, use the special statements provided in your software's analysis procedure to perform subgroup analyses.

We can use `subset` to produce correct variance estimates.

```{r}
nhanes<-subset(nhanes_all,svy_subpop_htn == 1)
```


